# Reproducible Research: Peer Assessment 1


## Loading and preprocessing the data
```{r echo = TRUE}
rowdata <- read.csv(unz(description="activity.zip", filename="activity.csv"), stringsAsFactors=F, colClasses=c(NA, "Date", NA))
str(rowdata)
head(rowdata)
summary(rowdata)
```

## What is mean total number of steps taken per day?
```{r echo = TRUE}
daytotal <- aggregate(steps ~ date, rowdata, sum)
hist(daytotal$steps, main="Total number steps per day")
```

The median of steps per day is  **`r sprintf("%.0f", median(daytotal$steps))`** (code used to compute:`sprintf("%.0f", median(daytotal$steps))`)  
The mean of steps per day is    **`r sprintf("%.0f", mean(daytotal$steps))`** (code used to compute:`sprintf("%.0f", mean(daytotal$steps))`)  


## What is the average daily activity pattern?
```{r echo = TRUE}
intervaltotals <- aggregate(steps ~ interval, rowdata, mean)
plot(intervaltotals, type="l", main="Average steps number via daytime")
```

Maximum interval is **`r intervaltotals[which(intervaltotals$steps==max(intervaltotals$steps)),1]`** (code used to compute:`intervaltotals[which(intervaltotals$steps==max(intervaltotals$steps)),1]`)


## Imputing missing values
Total number of missing values in the dataset is `r sum(is.na(rowdata$steps))` (code used to compute:`sum(is.na(rowdata$steps))`)

There are simple strategy for filling NA values:  
Take average for this interval for over all days.

```{r echo = TRUE}
df <- data.frame(rowdata)
df <- merge(df, intervaltotals, by.x="interval", by.y="interval", all.x=T, all.y=F)
na_idx <- which(is.na(df$steps.x))
df[na_idx, "steps.x"] <- df[na_idx, "steps.y"]
df <- data.frame(df[, c("date", "interval", "steps.x")])
colnames(df) <- c("date", "interval", "steps")
daytotal_f <- aggregate(steps ~ date, df, sum)
hist(daytotal_f$steps, main="Total number steps per day for filled NA's")
```

The median of steps per day (with filled NA's) is  **`r sprintf("%.0f", median(daytotal_f$steps))`** (code used to compute:`sprintf("%.0f", median(daytotal_f$steps))`)  
The mean of steps per day (with filled NA's) is    **`r sprintf("%.0f", mean(daytotal_f$steps))`** (code used to compute:`sprintf("%.0f", mean(daytotal_f$steps))`)  

It seems there are no influence of filling NA's to mean, medium and histogram.


## Are there differences in activity patterns between weekdays and weekends?
```{r echo = TRUE}
df$cal_typen <- factor(is.element(weekdays(df$date), c("Sunday", "Saturday")), labels = c("weekday", "weekend"))
par(mfcol=c(2,1), mar=c(0, 4, 4, 2))
plot(aggregate(steps~interval, df[df$cal_type=='weekday', ], mean), type="l", xlab=NA, ylab="Weekdays", xaxt="n")
par(mar=c(5, 4, 0, 2))
plot(aggregate(steps~interval, df[df$cal_type=='weekend', ], mean), type="l", ylab="Weekends")
```

It looks that weekends more 'flat' than weekdays (which have max aprox 8:35 am)
